---

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Shop Sales for Common Mobile In Egypt
========================================================



```{r echo=FALSE, message=FALSE, warning=FALSE, packages}


library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)
library(mapproj)
library(source.gist)
library(scales)
library(memisc)
library(GGally)
library(dplyr)
library(tidyr)
library(RColorBrewer)
library(reshape2)
library(gridExtra)
library(psych)
library(ggalt)
library(directlabels)
library(forcats)
library(ggrepel)
library(scales)

```


```{r echo=FALSE, Load_the_Data}
# Load the Data
setwd('D:/Udacity/P6')

mob <- read.csv('Egypt_mobile_Jan2018.csv')

```


> This dataset is about shop sales for mobile phone in Egypt containing
the prices,sellout transaction and other attributes of 
almost 200 famous Mobile that sold in 1700 in Jan 2018 shop

# Univariate Plots Section


```{r message=FALSE, warning=FALSE}
dim(mob)
str(mob)


```



Our dataset consists of 17 variables, with almost 26,000 observations.


```{r}
levels(mob$channel)
mob$channel <- factor(mob$channel,
                      levels = c('Hyper Market','Chain store',
                                 'Independent Shop'))

levels(mob$channel)
```


Reorder the levels of the channel from big (Hyper) to small (Independent)

```{r message=FALSE, warning=FALSE}
ggplot(data = mob , aes(x = price))+
  geom_histogram(binwidth = 800)+
  scale_x_continuous(breaks = seq(0,27000,2000))+
  xlab('Price')

ggplot(data = mob , aes(x = price))+
  geom_histogram(bins  = 30)+
  scale_x_log10(breaks=c(1000,1700,3800,6000,8000,10000))+
  xlab('Price')

summary(mob$price)
```


The tranformed price distribution appears bimodal with the price peaking
around 1700 or so and again at 3800 I wonder what this plot looks like across
the  variables of camera_mb, size_in_inch, ram, and storage.


```{r message=FALSE, warning=FALSE}
ggplot(data = mob , aes(x = ram))+
  geom_histogram(binwidth = 1)+
  scale_x_continuous(breaks = seq(0,6,1))+
  xlab('Ram In GB')+
  ggtitle('Ram Count')


ggplot(data = mob , aes(x = storage))+
  geom_histogram(binwidth = 4)+
  scale_x_continuous(breaks = c(1,2, 4, 8,16,32,64,128,256))+
  xlab('Storage In GB')+
  ggtitle('Storage Count')


ggplot(data = mob , aes(x = camera_mb))+
  geom_histogram(binwidth = 3)+
  scale_x_continuous(breaks = seq(1,23,3))+
  xlab('Camera In Mega Pixil')+
  ggtitle('Camera Count')


ggplot(data = mob , aes(x = size_in_inch))+
  geom_histogram()+
  scale_x_continuous(breaks = seq(0,10,.5))+
  xlab('Size')+ggtitle('Size Count')
```



Ram size play a big part in the price for each device

```{r message=FALSE, warning=FALSE}

ggplot(data = subset(mob,ram > 4) , aes(x = price))+
  geom_histogram(binwidth = 3000)+
  scale_x_continuous()+
  xlab('Price')+ggtitle('Price of Big Ram')

summary(subset(mob,ram > 4 ,select=c(price)))

ggplot(data = subset(mob,ram <= 4) , aes(x = price))+
  geom_histogram()+
  scale_x_continuous()+
  xlab('Price')+ggtitle('Price of Low Ram')

summary(subset(mob,ram <= 4 ,select=c(price)))

```

As we can see the price range for the ram exeed 4 GB and below it

```{r message=FALSE, warning=FALSE}

# sort brand before histogram
brand_count = sort(table(mob$brand_name), decreasing = T)

mob$brand_name = ordered(mob$brand_name ,levels = names(brand_count))

ggplot(data = mob , aes(brand_name))+
  geom_histogram(stat = 'count')+ coord_flip() + 
  ylab('Brand Count')+
  ggtitle('Mobiles')

ggplot(data = mob , aes(connection_band))+
  geom_histogram(stat="count")+
  ggtitle('Connectivity Generation')+
  xlab('Connection Band')
```

In the mobile brand graph we can see that most of the sales quantity came from
samsung then huawei



```{r}
names(mob)
shop_data <- mob %>%
  group_by(shop_id,governorate,latitude,longitude,channel,brand_name)  %>%
  summarise(ttl_quantity = sum(sellout),
            ttl_amount = sum(sellout * price)) %>%
  arrange(shop_id)



shop_data_qnt_wide = dcast(shop_data, shop_id + governorate + latitude +
                         longitude + channel ~ brand_name,
                       value.var="ttl_quantity", fun.aggregate=sum)

shop_data_subtotal = mob %>%
  group_by(shop_id,governorate,latitude,longitude,channel)  %>%
  summarise(ttl_quantity = sum(sellout),
            ttl_amount = sum(sellout * price)) %>%
  arrange(governorate,shop_id)

str(shop_data, give.attr = FALSE)
str(shop_data_subtotal, give.attr = FALSE)
str(shop_data_qnt_wide, give.attr = FALSE)




```


Our Shops are devided to 3 main Channels


```{r message=FALSE, warning=FALSE}
ggplot(data = shop_data_subtotal , aes(x = channel))+
  geom_histogram(stat="count",binwidth = 1)+
  ggtitle('Channels')+
  xlab('Channel')

table(shop_data_subtotal$channel)
```


As we want to summarize the transactions to each shop
we will summary the transactions for each shop



```{r message=FALSE, warning=FALSE}

# sort governorate before histogram
gov_count = sort(table(shop_data_subtotal$governorate), decreasing = T)

shop_data_subtotal$governorate = ordered(shop_data_subtotal$governorate ,
                                         levels = names(gov_count))

ggplot(data = shop_data_subtotal ,
       aes(x = governorate ))+
  geom_histogram(stat="count") + coord_flip() + 
  ylab('Shop Count')


ggplot(data = shop_data_subtotal , aes(x = ttl_quantity))+
  geom_histogram(binwidth = 5)+
  coord_cartesian(xlim = c(0,300))+ 
  ylab('Shop Count') + xlab('Quantity/PCS')

summary(shop_data_subtotal$ttl_quantity)

amount_p =ggplot(data = shop_data_subtotal , aes(x = ttl_amount))+
  geom_histogram() + xlab('Amount')
  # coord_cartesian(xlim = c(0,3000000))
amount_log_p = amount_p + scale_x_log10() + xlab('Amount Log')

grid.arrange(amount_p,amount_log_p,ncol = 1)

summary(shop_data_subtotal$ttl_amount)

```


# Univariate Analysis



### What is the structure of your dataset?

This dataset is about most usable mobile phone in Egypt containing the prices,
sellout transaction and other attributes of 
almost 200 famous Mobile that sold in 1700 shop 

(Biggest) ------> (Smallest)
Channel : (Hyper Market (bigger), Chain store, Independent Shop (Small))

### What is/are the main feature(s) of interest in your dataset?
The main Features in this data are :
1-The Amount of the sales and quantity in each shop.
I'd like to compare each geogrfic location with its sales
2-The best selling mobile phone and
what is the price segment that make more sales
3-What could effict the price of each model
### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
1-The channel type of each shop and the location of the shop whether its
on capital cities or rural
2-The ram,storage,screen size will help to determine the best mobile
### Did you create any new variables from existing variables in the dataset?
I added the amount of each transaction as the quantity soldout * the price
### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
I Created two main sets from this data 
1-The shop and its detail with total quantity of sales and the amount
2-The mobile sales with its detail

# Bivariate Plots Section

We have the longitude and latitude for our sample Shops

```{r}
ggplot(aes(x=longitude, y=latitude), data=mob) +
    geom_point(alpha = .008)


```


1. The more point is darker the more transaction happens 
2. Darker point are centralized cities or capital 


```{r}
mobile_data <- mob %>%
  group_by(model_id,model_name,brand_name,released_year,released_month,
           connection_band,size_in_inch,camera_mb,storage,ram,price)  %>%
  summarise(ttl_quantity = sum(sellout),
            n = n()) %>%
  arrange(brand_name,model_name)
mobile_data$ttl_amount <- (mobile_data$ttl_quantity * mobile_data$price)
str(mobile_data,give.attr = FALSE)


```


```{r echo=FALSE, Bivariate_Plots}


pairs.panels(mob[,c(4,7,8,9,10,11,12,14)],bg=c("blue","red","yellow"),
             pch=21,lm=TRUE)

pairs.panels(mobile_data[,c(6:12,14)],bg=c("blue","red","yellow"),
             pch=21,lm=TRUE)


```


From this data we notice that correlations between the price and the ram ,
storage are near to be strong while its mid in the camera quality


```{r}
ggplot(data = mob,
       aes(x = ram ,y = price ))+
  geom_point(alpha = .05, position = position_jitter(h = 0))

cor.test(mob$ram, mob$price)

ggplot(data = mob,
       aes(x = storage ,y = price ))+
  geom_point(alpha = .05, position = position_jitter(h = 0))+
  scale_x_continuous(breaks = c(4,8,16,32,64,128,256))

cor.test(mob$storage, mob$price)
```

The tall vertical strips indicate Storage and Ram values are mostly integers.
Adding jitter, transparency, and changing the plot limits
lets us see the slight correlation between table and price.


```{r message=FALSE, warning=FALSE}
Palette <- c('#003399','#f02f53','#ff664f','#b2ae85','#66CCFF','#4c4c4c',
             '#ffef96','#00a86b','#CCFFCC','#c2e8c8','#b61e98','#ffbcc8')
theme_set(theme_classic())

mobile_data$price.bucket <- cut(mobile_data$price,breaks =
                                  c(400,1500,3000,4000,5000,6000,10000,26000))

ggplot(data = mobile_data,
       aes(x = price ,y = ttl_quantity ))+
  geom_point(aes(color = price.bucket), stat = 'summary' , fun.y = sum )+
  guides(size = F, fill = guide_legend(override.aes = list(size=3)))+
  ylab('Quantity/PCS')+
  labs(color = "Price Range")

ggplot(data = mobile_data,
       aes(x = price ,y = ttl_quantity ))+
  geom_point(aes(color = price.bucket), stat = 'summary' , fun.y = sum )+
  ylab('Quantity/PCS')+
  scale_x_continuous(breaks = seq(0,6000,1000) , limits = c(400,6000))+
  guides(size = F, fill = guide_legend(override.aes = list(size=3)))+
  labs(color = "Price Range")


ggplot(mobile_data, aes(brand_name))+
  geom_bar(aes(fill=price.bucket), width = 0.5) + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) +
  labs(title ="Brand Model Prices Chart", 
       subtitle ="Brands", 
       fill = "Price Range")



ggplot(mobile_data, aes(x = "", y = ttl_quantity,
                        fill = fct_inorder(brand_name))) +
       geom_bar(width = 1, stat = "identity") +
       coord_polar("y", start = 0, direction = -1) + theme_void()+
       geom_label_repel(aes(label = ''),
                        size=5, show.legend = F, nudge_x = 5) +
       guides(fill = guide_legend(title = "Brand"))+

  scale_fill_manual(values= Palette )

# ggplot(data = mobile_data)+
#   geom_bar(aes(x = "", y = ttl_quantity, fill = brand_name),
#            stat ="identity", width = 1)+
#   coord_polar("y", start=0, direction = -1)+
#   theme_void()+
#        guides(fill = guide_legend(title = "Brand"))+
#   scale_fill_manual(values = Palette )

```


As we can see from this figure that the most of the sales are for the mobiles
below 6000 pound and most of the sales came from Samsung then Huawei

Next, I will look at how is the sales on these shops and where it is on
geographic map and how its distributed through different channels and which
brand has the most sales.

```{r message=FALSE, warning=FALSE}
p_channel_cnt = ggplot(data = shop_data_subtotal , aes(x = channel))+
  geom_histogram(stat="count",binwidth = 1)+
  ggtitle('Channels')+xlab('Channel')+ylab('Count Shops')

p_amount_chnl = ggplot(data = shop_data_subtotal ,
                       aes(x =channel ,y = ttl_amount))+
  geom_boxplot()+
  ggtitle('Amount By Channel')+xlab('Channel')+ylab('Amount')

grid.arrange(p_channel_cnt,p_amount_chnl,ncol = 1)

prop.table(table(shop_data_subtotal$channel))

sum(subset(shop_data_subtotal,channel != 'Hyper Market' ,
           select = c('ttl_amount')))/sum(shop_data_subtotal$ttl_amount)


ggplot(data = subset(shop_data_subtotal,channel != 'Hyper Market') ,
       aes(x =channel ,y = ttl_amount))+
  geom_boxplot()+scale_y_continuous(limits = c(0,3000000))+
  ggtitle('Amount By Channel (Exclude Hyper)')+xlab('Channel')+ylab('Amount')
```


Despite that the hypermarket shops not reach to 1 % but it controls most of
sales volume with amount 88%


```{r message=FALSE, warning=FALSE}

ggplot(data = mob,
       aes(x =price ,y =sellout ))+
  geom_point(alpha = .08)+
  scale_x_continuous(breaks = seq(0,26000,2000))+
  coord_cartesian(ylim = c(0,100))

# ggplot(data = shop_data ,
#        aes(x =brand_name ,y =ttl_amount ))+
#   geom_boxplot()+
# 
#   ggtitle('Brand Amount')+
#   ylab('Amount')+xlab('Brand')



ggplot(data = subset(shop_data,channel != 'Hyper Market'),
       aes(x =brand_name ,y =ttl_amount ))+
  geom_boxplot()+
  coord_cartesian(ylim = c(0,250000))+
  ggtitle('Brand Amount (Exclude Hyper Market)')+
  ylab('Amount')+xlab('Brand')

ggplot(data = subset(shop_data,channel == 'Hyper Market'),
       aes(x =brand_name ,y =ttl_amount ))+
  geom_boxplot()+
  coord_cartesian(ylim = c(0,5500000))+
  ggtitle('Brand Amount')+
  ylab('Amount')+xlab('Brand')



summary(shop_data[shop_data$channel != 'Hyper Market',c('ttl_amount')])
summary(shop_data[shop_data$channel == 'Hyper Market',c('ttl_amount')])


```

These graphs shows us that the most sales is for the mobiles below 6000 EGP
and most of the sales comes from samsung specially from Hyper market as there
were a gift for each mobile sold


Load the maps

```{r message=FALSE, warning=FALSE}
egypt <- get_googlemap("Egypt",zoom=6,maptype="terrain",source="google",
                       size = c(640,515),scale = 2)

alex <- get_googlemap("alexandria",zoom=11,maptype="terrain",source="google",
                      size = c(640,440),scale = 2)


cairo <- get_googlemap("cairo",zoom=10,maptype="terrain",source="google",
                       size = c(640,440),scale = 2)
```


```{r}
ggmap(egypt)+
  geom_point(data = mob , aes(x =longitude ,y =latitude ) , color = "#0571b0",
             alpha = .5,size = sqrt(mob$sellout/pi)/4 )

ggmap(egypt) +
  geom_density2d(data=shop_data_subtotal,aes(x=longitude,y=latitude), bins=30) +
  stat_density2d(data=shop_data_subtotal,aes(x=longitude,y=latitude,
                                             fill=..level..,alpha=..level..),
                 geom='polygon')
```


As we see from the above that the most sales are happend in two main cities 
The biggest one is the Cairo (Capital of Egypt in the center) and Alexandria 
as these are urban cities and low volume in other cities as they are
rural cities


```{r message=FALSE, warning=FALSE}
ggmap(cairo)+
  geom_point(data = mob , aes(x =longitude ,y =latitude ) , color = "#0571b0",
             alpha = .3,size = sqrt(mob$sellout/pi) )+
  ggtitle('Cairo Quantity Sales')


ggmap(alex)+
  geom_point(data = mob , aes(x =longitude ,y =latitude ) , color = "#0571b0",
             alpha = .5,size = sqrt(mob$sellout/pi) )+
  ggtitle('Alexandria Quantity Sales')
```


# Bivariate Analysis


### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?
The sales volume increase in Hypermarkets and It controle the market while its
not reach 1% of total market


### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?
As the Market is bigger the amount and quantity of sales 


### What was the strongest relationship you found?
The relationship between the ram size and the price the larger ram size
the larger price and same for the storage

# Multivariate Plots Section

```{r}
ggplot(data = shop_data, aes(x =brand_name ,y =ttl_amount)) +
  geom_boxplot()+
  facet_wrap(~channel , ncol=1)+
  ggtitle('Brand Amount')+
  ylab('Amount')+xlab('Brand')
```


As we can see that sales are booming in hyper market specially
for samsung mobiles


Ram variety for each brand

```{r echo=FALSE, message=FALSE, warning=FALSE}


ggplot(data = mobile_data , aes(x =ram ,y =price ))+
  geom_point(aes(fill = brand_name), stat = 'summary', fun.y = mean ,
             size = 2 ,pch = 21)+
  guides(size = F, fill = guide_legend(override.aes = list(size=5)))+
  scale_fill_manual(values = Palette)

ggplot(data = mobile_data , aes(x =ram ,y =price ))+
  geom_point(aes(fill = brand_name , size = sqrt(mobile_data$ttl_amount)),
             pch = 21 , alpha = .5)+
  labs(size = 'Amount')+
  guides(size = F, fill = guide_legend(override.aes = list(size=5)))+
  scale_fill_manual(values = Palette )

ggplot(data = mobile_data , aes(x =ram ,y =price ))+
  geom_point(aes(fill = brand_name , size = sqrt(mobile_data$ttl_amount)),
             pch = 21 , alpha = .5)+
  labs(size = 'Amount')+
  guides(size = F, fill = guide_legend(override.aes = list(size=5)))+
  scale_fill_manual(values = Palette ) +
  facet_wrap(~brand_name)
```



```{r message=FALSE, warning=FALSE}
ggmap(cairo)+
  geom_point(data = shop_data_subtotal , aes(x =longitude ,y =latitude  ,
             colour = channel,
             alpha = .5,size = (sqrt(shop_data_subtotal$ttl_amount/pi))) )+
  labs(size="Amount" , alpha = 'Transperancy' , channel = 'Channel')+
  scale_size_continuous(range=c(1,7)) +
  ggtitle('Cairo Sales Amount')

ggmap(alex)+
  geom_point(data = shop_data_subtotal , aes(x =longitude ,y =latitude  ,
             colour = channel,
             alpha = .5,size = (sqrt(shop_data_subtotal$ttl_amount/pi))) )+
  labs(size="Amount" , alpha = 'Transperancy' , channel = 'Channel')+
  scale_size_continuous(range=c(1,7)) +
  ggtitle('Alexandria Sales Amount')
```



```{r message=FALSE, warning=FALSE}
xbreaks = c(1000, 1500, 2000, 3000, 4000, 5000, 6000, 10000,15000,28000)
ybreaks = c(100000, 500000, 1000000, 5000000, 10000000, 20000000, 40000000,
            80000000)
ggplot(data = mobile_data, 
       aes(x = price, y = ttl_amount)) + 
  geom_point(aes(fill = brand_name, size = sqrt(ttl_quantity/pi)), 
             pch = 21 , alpha = .7) + 
  ggtitle("Mobile Sales") +
  xlab("Price") +
  ylab("Amount In EGP")+
  scale_x_log10(breaks = xbreaks,
                labels = comma(xbreaks) , limits = c(800,8000)) +
  scale_y_log10(breaks = ybreaks,
                labels = comma(ybreaks)) +

  scale_size_continuous(range=c(1,12)) +
  guides(size = F, fill = guide_legend(override.aes = list(size=5))) +
  scale_fill_manual(values= Palette)


```



```{r}
brand_summary <- mob %>%
  group_by(brand_name)  %>%
  summarise(ttl_quantity = sum(sellout),
            avg_price = mean(price),
            n = n()) %>%
  arrange(brand_name)
brand_summary$ttl_amount <- (brand_summary$ttl_quantity *
                               brand_summary$avg_price)
str(brand_summary,give.attr = FALSE)
```



```{r}
xbreaks = c(1000, 1500, 2000, 3000, 4000, 5000,15000)
ybreaks = c(100000, 500000, 1000000, 5000000, 10000000, 20000000, 40000000,
            80000000,150000000,300000000,600000000)
ggplot(data = brand_summary, 
       aes(x = avg_price, y = ttl_amount)) + 
  geom_point(aes(fill = brand_name, size = sqrt(ttl_quantity/pi)), 
             pch = 21 , alpha = .7) + 
  ggtitle("Mobile Sales") +
  xlab("Price") +
  ylab("Amount In EGP")+
  scale_x_log10(breaks = xbreaks,
                labels = comma(xbreaks) ) +
  scale_y_log10(breaks = ybreaks,
                labels = comma(ybreaks)) +

  scale_size_continuous(range=c(1,12)) +
  guides(size = F, fill = guide_legend(override.aes = list(size=5))) +
  scale_fill_manual(values= Palette)
```


If we take the average price for each brand and measuere the sales amount for
each brand we could see that samsung has the lead of sales amount and huawei
and oppo try to follow up

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?
yes having a varaities of models for each price segment leads to better sales
and win bigger market share

### Were there any interesting or surprising interactions between features?
yes all the mobiles feature with the same ram and storage have almost same
price except for apple that plays in a vary big price range comparing to others
### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary



### Plot One

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggmap(egypt) +
  geom_density2d(data=shop_data_subtotal,aes(x=longitude,y=latitude), bins=30) +
  stat_density2d(data=shop_data_subtotal,aes(x=longitude,y=latitude,
                                             fill=..level..,alpha=..level..),
                 geom='polygon')
```


### Description One
The sales are centralized in the capital urban cities In Cairo and Alexandria
while in rural area are small at the same time the income level on the urban
and the culture for them deffer in the indevedual behaviour of consuming

### Plot Two

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggmap(cairo)+
  geom_point(data = shop_data_subtotal , aes(x =longitude ,y =latitude  ,
             colour = channel,
             alpha = .5,size = (sqrt(shop_data_subtotal$ttl_amount/pi))) )+
  labs(size="Amount" , alpha = 'Transperancy' , channel = 'Channel')+
  scale_size_continuous(range=c(1,7)) +
  ggtitle('Cairo Sales Amount')
```


### Description Two
Most of the sales quantity are in the Hyper big market as it attract
the consumer with its discount specially in January the sales
season (Black friday)
and it has the variaities that satisfiy each consumer price segment

### Plot Three

```{r echo=FALSE, message=FALSE, warning=FALSE}
xbreaks = c(1000, 1500, 2000, 3000, 4000, 5000,15000)
ybreaks = c(100000, 500000, 1000000, 5000000, 10000000, 20000000, 40000000,
            80000000,150000000,300000000,600000000)
ggplot(data = brand_summary, 
       aes(x = avg_price, y = ttl_amount)) + 
  geom_point(aes(fill = brand_name, size = sqrt(ttl_quantity/pi)), 
             pch = 21 , alpha = .7) + 
  ggtitle("Mobile Sales") +
  xlab("Price") +
  ylab("Amount In EGP")+
  scale_x_log10(breaks = xbreaks,
                labels = comma(xbreaks) ) +
  scale_y_log10(breaks = ybreaks,
                labels = comma(ybreaks)) +

  scale_size_continuous(range=c(1,12)) +
  guides(size = F, fill = guide_legend(override.aes = list(size=5))) +
  scale_fill_manual(values= Palette)
```


### Description Three

compete in each price segment and with good advertising makes samsung lead
the sales and have an average price of 4000 and good reputation

------

# Reflection
It was a great time work on this project I used some wrangling and scraping
skills to get the mobile specs and info from http://gsmarena.com and match
each mobile specs with this data set, but I miss one big variable that could
clear more the idea and help in this analysis and that's the processor type
and speed as I think the processor and ram play a big part in the Mobile price
which will effect at the end the sales portion for each shop
